03 Data Vizualization

### 2022-06-17 03_data_viz.Rmd
assimilation efficiency histogram

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type,
      label = round(u_d_mc, 2)
      )
  ) +
    geom_point(size = 3) +
    geom_errorbar(aes(
      xmin = u_d_mc - (0.5 * su_d_mc),
      xmax = u_d_mc + (0.5 * su_d_mc)),
      width = 0,
      size = 1.1
      ) +
    #Uncomment to show generation times
    geom_text(
      nudge_x = 0.05
    ) +
    coord_cartesian(xlim = c(0, 0.175)) +
    scale_fill_manual(values = c("black", color_choice)) +
    scale_color_manual(values = c("black", color_choice)) +
    theme_classic() +
    labs(x = TeX("Turnover ($day^{-1}$)"),
         title = terrain_choice) +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.y = element_blank(),
      strip.background = element_blank(),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x = element_line(linetype = "dotted")
    )

@@

# ggsave(
#   plot = p_turnover,
#   filename = "fig_output/turnover_plot.pdf",
#   device = cairo_pdf, # Need this for greek symbols to render correctly
#   width = 11,
#   height = 4
#   )

@@

cowplot::save_plot(filename = "fig_output/abundance_v_turnover_1p.pdf",
                   plot = p_abundance_v_turnover,
                   base_height = 6,
                   base_width = 8)
```

@@

>>>>

### Load d2H assimilation data

```{r}
d2H_assim <- read_xlsx("data/d2H_data_isotope_measurements.xlsx", sheet = 'lipids')
```

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type,
      label = round(u_d_mc, 4)
      )
  ) +
    geom_point(size = 3) +
    geom_errorbar(aes(
      xmin = u_d_mc - (0.5 * su_d_mc),
      xmax = u_d_mc + (0.5 * su_d_mc)),
      width = 0,
      size = 1.1
      ) +
    #Uncomment to show generation times
    # geom_text(
    #   nudge_x = 0.05
    # ) +
    coord_cartesian(xlim = c(0, 0.175)) +
    scale_fill_manual(values = c("black", color_choice)) +
    scale_color_manual(values = c("black", color_choice)) +
    theme_classic() +
    labs(x = TeX("Turnover ($day^{-1}$)"),
         title = terrain_choice) +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.y = element_blank(),
      strip.background = element_blank(),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x = element_line(linetype = "dotted")
    )

@@

ggsave(
  plot = p_turnover,
  filename = "fig_output/turnover_plot.pdf",
  device = cairo_pdf, # Need this for greek symbols to render correctly
  width = 11,
  height = 4
  )

@@

# cowplot::save_plot(filename = "fig_output/abundance_v_turnover_1p.pdf",
#                    plot = p_abundance_v_turnover,
#                    base_height = 6,
#                    base_width = 8)
```

@@

## (PASSING) Assimilation efficiency histogram

```{r}
# Find Fatty acid analytes manually

fas_in_d2H_assim <- d2H_assim %>% 
  filter(str_detect(Analyte, "acid") |
           str_detect(Analyte, "ate")) %>% 
  pull(Analyte) %>% 
  unique()

d2H_assim_lm <- d2H_assim %>% 
  # Select columns of interest
  select(
    org_id,
    exp_id,
    Analyte,
    `Water dD`,
    `Lipid dD`
  ) %>% 
  # Filter to only look at FAs
  filter(Analyte %in% fas_in_d2H_assim) %>% 
  drop_na() %>% 
  # Group by organism, experiment, analyte
  group_by(
    org_id,
    exp_id,
    Analyte
  ) %>% 
  # Filter out samples with three or fewer observations
  # (so that we can do a linear model)
  filter(n() > 3) %>% 
  tidyr::nest(
    data = c(`Water dD`, `Lipid dD`)
  ) %>% 
  mutate(
    fit = purrr::map(data, ~lm(`Lipid dD` ~ `Water dD`, data = .x)),
    estimates = purrr::map(fit, broom::tidy),
    summary = purrr::map(fit, broom::glance)
  ) %>% tidyr::unnest(estimates) %>%
  filter(term == "`Water dD`") %>% 
  filter(estimate >= 0,
         estimate <= 1) %>% 
  select(c(term, estimate))

mean_assim <- d2H_assim_lm %>% pull(estimate) %>% mean(na.rm = TRUE)
se_assim <- d2H_assim_lm %>% pull(estimate) %>% sd(na.rm = TRUE)

```{r}
p_d2H_assim_lm <- d2H_assim_lm %>% 
  ggplot(aes(x = estimate)) +
  geom_histogram(binwidth = 0.1,
                 color = tundra_color,
                 fill = tundra_color) +
  geom_vline(xintercept = mean_assim,
             linetype = "dotted") +
  geom_errorbar(
    aes(
      xmin = mean_assim - (0.5*se_assim),
      xmax = mean_assim + (0.5*se_assim),
      y = 16
        )) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
  coord_cartesian(ylim = c(0, 26),
                  expand = FALSE) +
  labs(x = "Assimilation Efficiency",
       y = "Count") +
  theme_classic()
p_d2H_assim_lm

# cowplot::save_plot(
#   plot = p_d2H_assim_lm,
#   filename = "fig_output/assim_efficiency.pdf",
#   base_height = 4,
#   base_width = 4
# )
```
